Dynamic Modeling of the Human Coagulation Cascade using Reduced Order Effective Kinetic Models

### 2015-02-20 processes-69103_review_response/processes-69103.tex
Changes in discussion

The performance of the proof of principle coagulation model was impressive given its limited size. The most detailed mechanistic model of coagulation is the one by Luan and co-workers built  with 193 proteins and protein complexes that are interconnected by 301 reactions \citep{2010_luan_varner_MolBioSys}. Akin to the hybrid model this mechanistic used the normal thrombin data and hemophilia data from Allen \emph{et al.} \citep{ALLEN2006}. However unlike the mechanistic model we used this data for validation rather than training. Results from our model are surprisingly comparable to the training simulations of the mechanistic model. The initiation time and amplification of thrombin signal were accurately predicted in the normal case whereas in the hemophilia case we correctly predict the initiation time but slightly over predict the amplification signal. This performance is nearly similar to that of the detailed mechanistic model with 301 reactions. Despite the impressive performance, there are several issues that could be further explored. First, the prediction of initiation time should be investigated. 

>>>>

A number of mathematical models and computational simulations concerning coagulation dynamics have been based on the Hockin-Mann model of coagulation.

The performance of the proof of principle coagulation model was impressive given its limited size. The most detailed mechanistic model of coagulation is the one by Luan and co-workers built  with 193 proteins and protein complexes that are interconnected by 301 reactions \citep{2010_luan_varner_MolBioSys}. Akin to the hybrid model this model used normal thrombin data and hemophilia data from Allen \emph{et al.} \citep{ALLEN2006}. However unlike the mechanistic model we used this data for validation rather than training. Results from our model are surprisingly comparable to the training simulations of the mechanistic model. The initiation time and amplification of thrombin signal were accurately predicted in the normal case whereas in the hemophilia case we correctly predict the initiation time but slightly over predict the amplification signal. This performance is nearly similar to that of the detailed mechanistic model with 301 reactions. Despite the impressive performance, there are several issues that could be further explored. First, the prediction of initiation time should be investigated. 
